Test susieI using chr17 to 22

### 2020-09-14 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
susieI plots

  m <- cbind(df[,"pi1.gene_mr.ash2"]/df[,"pi1.SNP_mr.ash2"], 1:nrow(df), 1 + 1:nrow(df)/nrow(df)/3)
  st <-  cbind(df[,"pi1.gene_susietruth"]/df[,"pi1.SNP_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"]/df[,"pi1.SNP_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]/df[1,"pi1.SNP_truth"]
  dfp <- rbind(m,st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "Enrichment (gene/snp)", xaxt = "n", xlab="", xlim = c(0.8, 3.5),frame.plot=FALSE, ylim = c(0, max(dfp[,1],t, 150) *1.05))
  axis(side=1, at=1:3, labels = FALSE, tick = F)
  text(x=1:3, 0, labels = c("mr.ash2", "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h= t, lty = 2, col= "darkgreen", lwd=1.5)
  grid()
}
```

>>>>

  m <- cbind(df[,"pi1.gene_mr.ash2"]/df[,"pi1.SNP_mr.ash2"], 1:nrow(df), 1 + 1:nrow(df)/nrow(df)/3)
  st <-  cbind(df[,"pi1.gene_susietruth"]/df[,"pi1.SNP_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"]/df[,"pi1.SNP_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]/df[1,"pi1.SNP_truth"]
  dfp <- rbind(m,st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "Enrichment (gene/snp)", xaxt = "n", xlab="", xlim = c(0.8, 3.5),frame.plot=FALSE, ylim = c(0, min(max(dfp[,1],t) *1.05, 150)))
  axis(side=1, at=1:3, labels = FALSE, tick = F)
  text(x=1:3, 0, labels = c("mr.ash2", "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h= t, lty = 2, col= "darkgreen", lwd=1.5)
  grid()
}
```
